Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

\section{Evolving Social Network}
In some related research on evolving graphs, the time dimension is represented
by constructing a sequence of graphs $\{G_t(V_t,E_t)\}$ on different time
spots $t$. This model is highly expressive and universal in mathematical
statement, thus we adopt in. However, we constrain the relation of
time-adjacent graphs in order to simplify the analysis and remain the highest
possible loyalty to the real data generation. We build the \textbf{pure growing
model}, which care about the new connection forming among vertices, neglecting
the anti-growing operations such as edge deletions. We assume the existence of
every connection will contribute to the metrics, even if the connection is
later erased, so we do not delete edges or nodes in our model, instead we could
add an decay mechanism to reduce the affect of old formed links, which will be
discussed in the next section. Note that in pure growing model, we will assign
every edge a timestamp, namely when the edge is created. And thus there could
be more than one edges between a pair of nodes, with different timestamp.

>>>>

\section{Evolving Social Network}
In some related research on evolving graphs, the time dimension is represented
by constructing a sequence of graphs $\{G_t(V_t,E_t)\}$ on different time
spots $t$. This model is highly expressive and universal in mathematical
statement, thus we adopt in. However, we constrain the relation of
time-adjacent graphs in order to simplify the analysis and remain the highest
possible loyalty to the real data generation. We build the \textbf{pure growing
model}, which cares about the new connection forming among vertices, neglecting
the anti-growing operations such as edge deletions. We assume the existence of
every connection will contribute to the metrics, even if the connection is
later erased. So we do not delete edges or nodes in our model, instead we could
add an decay mechanism to reduce the affect of old formed links, which will be
discussed in the next section. In pure growing model, we will assign every edge
a timestamp, namely what time the edge is created. Thus there could be more
than one edges between a pair of nodes with different timestamps.
